Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-06-28 paper/paper.tex
Fixing typo
But -> However

  In this paper, we show their functional correspondence and how to syntactically 
  transform small-step abstract abstract machines into big-step abstract definitional
  interpreters.
  The transformations include linearization, lightweight fusion, disentanglement, 
  refunctionalization, and finally transformation from CPS back to direct-style 
  with delimited control operators. 
  Linearization expresses nondeterministic choices by first-order data types, 
  after which refunctionalization transforms the first-order datatypes representing continuations
  into higher-order functions. 
  The refunctionalized AAM is an abstract interpreter written in continuation-passing style
  with two layers of continuation.

@@

Defining a language by building an interpreter for it can be traced to the very
early days of programming languages research \cite{McCarthy:1960:RFS:367177.367199,landin1966next, Reynolds:72}.
Nowadays, even undergraduate students in computer science learn how to define 
their own programming languages by building an interpreter.
But building a sound abstract interpreter remained an esoteric and difficult task 
until very recently.

>>>>

  In this paper, we show their functional correspondence and how to syntactically 
  transform small-step abstract abstract machines into big-step abstract definitional
  interpreters.
  The transformations include linearization, lightweight fusion, disentanglement, 
  refunctionalization, and finally transformation from CPS back to direct-style 
  with delimited control operators. 
  Linearization expresses nondeterministic choices by first-order data types, 
  after which refunctionalization transforms the first-order datatypes representing continuations
  into higher-order functions. 
  The refunctionalized AAM is an abstract interpreter written in continuation-passing style
  with two layers of continuations.

@@

Defining a language by building an interpreter for it can be traced to the very
early days of programming languages research \cite{McCarthy:1960:RFS:367177.367199,landin1966next, Reynolds:72}.
Nowadays, even undergraduate students in computer science learn how to define 
their own programming languages by building an interpreter.
However, building a sound abstract interpreter remained an esoteric and difficult task
until very recently.
